
\section{Goals}
% \todo[inline, backgroundcolor=kth-lightblue]{Mål}
% \todo[inline, backgroundcolor=kth-lightblue]{Skilj på syfte och mål. Syftet är att åstakomma en förändring i något. Målen är vad som konkret skall göras för att om möjligt uppnå den önskade förändringen (syfte). }

% \todo[inline]{State the goal/goals of this degree project.}

The project aims to create a secure, mountable filesystem which stores its data via online we services by taking advantage of the storage given to their users. This can be split into the following subgoals;
\begin{enumerate}
\item to create a free mountable filesystem where files can be stored, read, and deleted, % \todo[inline, backgroundcolor=kth-lightblue]{för att tillfredsställa problemägaren – industrin?}
\item for the system to be secure in the sense that even with access to the uploaded files and the software, the data is not readable without the correct decryption key, and, % \todo[inline, backgroundcolor=kth-lightblue]{för att tillfredsställa ingenjörssamfundet och vetenskapen – akademin) }
\item to analyze the throughput, dependability and reliability of the filesystem and compare to commercial distributed filesystems.
% \item to be able to store a useful\footnote{} amount of data % \todo[inline, backgroundcolor=kth-lightblue]{eventuellt, för att uppfylla kursmålen – du som student}
\end{enumerate}

\todo[inline]{In the following paragraph, I am trying to relay that the steganographic feature of the filesystem is not the goal, but rather a side effect of a publicly available data storage system. Is this a valid idea or should I rahter addess it some other way? Should I move it do be above the enumeration of subgoals? Or should it be a subgoal rather?}

A side effect of such a filesystem which creates posts that are, while encrypted, publicly available is a steganographic filesystem in the sense that the data is hidden in plain sight. An imminent subgoal is therefore also to achieve and analyze the deniability of the system.

% \todo[inline]{In addition to presenting the goal(s), you might also state what the deliverables and results of the project are.}
