\section{Online web services}
\label{sec:ows}
This section presents two \gls{OWS}s, Twitter (ยง\ref{subsec:ows_twitter}) and Flickr (ยง\ref{subsec:ows_flickr}), where one can create \mbox{free-tier} accounts. Both of these \gls{OWS}s offer \mbox{free-tier} accounts that can make numerous posts for free. These \glspl{OWS} each provide a \mbox{free-to-use} \gls{API} for \mbox{non-commercial} development. 

\subsection{Twitter}
\label{subsec:ows_twitter}
Twitter is a \mbox{micro-blog} online where users can sign up for a free account and create public posts (tweets) using text, images, and videos. Each post has a unique ID associated with it\,\cite{twitterTwitterIDs}. Text posts are limited to \num{280} characters while images can be up to \SI{5}{\mega\byte} and videos up to \SI{512}{\mega\byte}\,\cite{MediaBestPractices}. A post with images can contain up to four images in one post. There is also the possibility to send private messages to other accounts, where each message can contain up to \num{10000} characters and the same limitations apply to files (as stated above). Direct messages older than \num{30} days are not possible to retrieve via Twitter's \gls{API}\,\cite{RetrievingOlder302018}. However, it is possible to create threads of Twitter posts where multiple tweets can be associated in chronological order.

Twitter's \gls{API} defines technical limits on how many times certain actions can be executed by a user\,\cite{UnderstandingTwitterLimits}. A maximum of \num{2400} tweets can be sent per day, and this limit is further broken down into smaller limits at \mbox{semi-hourly} intervals. Hitting a limit means that the user account can no longer perform the actions that the limit represents until the time period has elapsed.

\subsection{Flickr}
\label{subsec:ows_flickr}
Flickr is a public image \& video hosting service used to store and share photos and videos. Unlike Twitter, a post on Flickr is based on an image or video. Optionally, the post can  have a title, a description, or both. However, the post must have exactly one photo or video. Flickr supports multiple image and video formats, including PNG and MP4\,\cite{FlickrUploadRequirements2022}. Size restrictions are set for each post, depending on the media type. Images uploaded to Flickr can be a maximum of \SI{200}{\mega\byte} and a video can be a maximum of \SI{1}{\giga\byte}. Furthermore, \mbox{free-tier} accounts can only have a total of \num{1000} photos or videos in their account. This corresponds to a maximum of \SI{200}{\giga\byte} of storage, if one stores only images or \SI{1}{\tera\byte} of storage if one only stores videos. A mix of images and videos can also be uploaded, which would mean that the maximum storage capacity would be between \SI{200}{\giga\byte} and \SI{1}{\tera\byte}. A Flickr Pro account has unlimited storage on Flickr but is still subject to the \mbox{per-item} limit of \SI{200}{\mega\byte}, and \SI{1}{\giga\byte} for images and videos, respectively\,\cite{flickrinc.UpgradeEverythingYou}. Flickr Pro costs between EUR~7.49 to EUR~5.49 per month, depending on the subscription time the user signs up for. The description of a post has a limit of \num{65535} characters according to Shhexy Corin\,\cite{FlickrHelpForum2009}. This has limit been verified through testing. The title of a post has also been discovered through testing to have a limit of 255 characters.

\Needspace*{16\baselineskip}
The images and videos uploaded to Flickr are stored in their original form \textbf{without any compression} and can be downloaded \textbf{by the user} as the same file as was uploaded\,\cite{flickrinc.DownloadPermissions}. Flickr also stores other formats of the file, such as thumbnails. User accounts can restrict who, other than the user, can download the original image. This restricts who can download the file and helps ensure that \mbox{no-one} else can read the original file data, but also requires the user to authenticate with Flickr to download the image; thus, it is impossible to download the image data anonymously. Even if the original image cannot be downloaded by anonymous users when such restrictions are set by the original uploader, these anonymous users can still download other versions of the image. However, the other versions of the image \textbf{do not contain the same data as the original image} but they look similar, potentially enabling reverse engineering of the original pixel data. As stated above, the original video can only be downloaded by the user\,\cite{flickrinc.DownloadPermissions}. Flickr does not state if it will always be possible for the user to download their original version of the uploaded image or video. Furthermore, Flickr states that it retains the right to remove user content from their service at any time\,\cite{flickrinc.FlickrTermsConditions2020}.

The Flickr \gls{API} defines a query limit of \num{3600} requests per hour per application across all \gls{API} calls\,\cite{flickrinc.FlickrFlickrDeveloper}. However, according to Sam Judson in 2013, this is not a hard limit\,\cite{WhatAreAPI2013}. Unfortunately, this source is from almost a decade ago. There is no official information from Flickr about what happens if you break the hourly request limit. The Flickr \gls{API} states that the \gls{API} is monitored with respect to additional factors as well\,\cite{flickrinc.FlickrFlickrDeveloper}. If abuse is detected, Flickr reserves the right to revoke the \gls{API}'s keys.