\section{Development environment specification}
\label{sec:dev_env}
Development of \gls{FFS} was done on a 15 inch 2016 year model Macbook Pro laptop with a \SI{2.6}{\giga\hertz} \mbox{Quad-Core} Intel Core i7 processor and \SI{16}{\giga\byte} \SI{2133}{\mega\hertz} LPDDR3 memory. The storage device of the computer was a \SI{250}{\giga\byte} \gls{SSD} running an encrypted \gls{APFS} partition as the filesystem. Apple claims that the \gls{SSD} has a read speed of \SI[per-mode = symbol]{3.1}{\giga\byte\per\second} and a write speed of \SI[per-mode = symbol]{2.2}{\giga\byte\per\second}. The computer used to develop FFS was running macOS.

Table~\ref{tbl:dev_env} presents the version of the libraries, APIs and tools used by FFS. FFS was developed using C++ and compiled using Apple clang. \gls{FFS} uses the ImageMagick Magick++ library\,\cite{ImageMagick2022} for image processing. macFUSE\,\cite{HomeMacFUSE} is used for \gls{FFS} to use the \gls{FUSE} \gls{API}. cURLpp\,\cite{barrette-lapierreCURLpp2022} is a cURL\,\cite{CurlCurl2022} C++ wrapper used by \gls{FFS} to make HTTP requests. libOauth\,\cite{Liboauth} is used by \gls{FFS} to sign and encode HTTP requests according to the OAuth\,\cite{barrette-lapierreCURLpp2022} standard. Flickcurl\,\cite{beckettFlickcurlLibraryFlickr} is a C library used by \gls{FFS} to communicate with parts of the Flickr \gls{API}. Crypto++\,\cite{CryptoLibraryFree} is a C++ library providing cryptographic schemes. \gls{FFS} uses Crypto++ to encrypt end decrypt the data stored in \gls{FFS}, and to derive the keys used in the encryption and decryption algorithm. 


\begin{table}[!ht]
	\begin{center}
		\caption{The versions of the libraries, APIs, and tools used by \gls{FFS}}
		\begin{tabular}{| l || c |}
			
			\hline

			\textbf{Library, API, or tool} & \textbf{Version}\\
			
			\hline
			\hline
			
				C++						& 20 \\
				Apple clang 			& 13.0.0\\
				Apple clang target		& x86\_64\-apple\-darwin21.4.0\\
				ImageMagick Magick++	& 7.1.0\-29\\
				macFUSE					& 4.2.5 \\
				FUSE API				& 26 \\
				cURLpp					& 0.8.1 \\
				libOauth				& 1.0.3 \\
				Flickcurl				& 1.26 \\
				Crypto++				& 8.6 \\
				macOS Monterey			& 12.5\\

			\hline
		\end{tabular}
		\label{tbl:dev_env}
	\end{center}

\end{table}

\gls{FFS} was developed for use on a single computer for simplicity, and the version used for the operating system, libraries, and tools were the most recent \mbox{up-to-date} versions when the development of the filesystem started. To avoid \mbox{re-writing} the source code to handle new \gls{API} designs, these versions remained the same throughout the development process.